Reasoning About a Machine with Local Capabilities

### 2018-05-06 toplas/paper.tex
Update TOPLS suggestion

\begin{toplas}
\section{Reasoning about programs on a capability machine}
\label{sec:reasoning}
\itoplassug{
  \begin{itemize}
  \item A section with the lemmas we use for reasoning about programs
    \begin{itemize}
    \item lemma 58, scall works. Include description of how it handles the
      common things in call and leaves the argumentation for callee code and
      continuation.
    \item lemma 59, malloc works. If this is included, we should probably also
      include the malloc specification.
    \item lemma 60, create closure works.
    \item Include a description about how the FTLR is used to reason about
      unknown code.
    \item Mention that this is a step on the way towards having a program logic,
      and then in the discussion discuss why a program logic for this language
      is not what we need.
    \end{itemize}
  \end{itemize}
}

>>>>

\begin{toplas}
\section{Reasoning about programs on a capability machine}
\label{sec:reasoning}
% \itoplassug{
%   \begin{itemize}
%   \item A section with the lemmas we use for reasoning about programs
%     \begin{itemize}
%     \item lemma 58, scall works. Include description of how it handles the
%       common things in call and leaves the argumentation for callee code and
%       continuation.
%     \item lemma 59, malloc works. If this is included, we should probably also
%       include the malloc specification.
%     \item lemma 60, create closure works.
%     \item Include a description about how the FTLR is used to reason about
%       unknown code.
%     \item Mention that this is a step on the way towards having a program logic,
%       and then in the discussion discuss why a program logic for this language
%       is not what we need.
%     \end{itemize}
%   \end{itemize}
% }
\itoplassug{add actual intro to this section.}
